Case study validations of automatic bullet matching

### 2018-11-21 index.Rmd
Fixing headings for intro, Methods sections
template update and yaml changes

authors: 
- name: Heike Hofmann, Ph.D.
  affiliation: Department of Statistics, Iowa State University
  thanks: 
    - This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement \#70NANB15H176 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, University of California Irvine, and University of Virginia.
    - The authors wish to thank Jim Hamby, Tylor Klep (Phoenix PD), and Melissa Nally and Kasi Kirksey (FSI Houston) for access to test set bullets. XXX Scanning. Hamby advice.

- name: Susan VanderPlas, Ph.D.
  affiliation: Department of Statistics, Iowa State University

keywords:
- random forest
- 3d microscopy
- toolmark

@@

bibliography: bibliography
biblio-style: apsr

output: 
  pdf_document:
    number_sections: false
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: template.tex
---

@@

# Introduction and Background

@@

## Automated Processing of 3D Scans

@@

## Statistics for Matching Aligned Signatures

@@

## Interpreting the Algorithm Score

@@

## Identification Errors and Algorithm Evaluation

@@

## Assessing Match Strength

>>>>

affiliation: 
- Department of Statistics, Iowa State University
- Center for Statistical Applications in Forensic Evidence (CSAFE), Iowa State University

authors: 
- name: Heike Hofmann
  degree: Doctor of Philosophy (Ph.D.)
- name: Susan VanderPlas
  degree: Doctor of Philosophy (Ph.D.)

funding: This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement \#70NANB15H176 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, University of California Irvine, and University of Virginia.

thanks: 
- The authors wish to thank Jim Hamby, Tylor Klep (Phoenix PD), and Melissa Nally and Kasi Kirksey (FSI Houston) for access to test set bullets. 
- XXX Scanning. 
- Thanks to Jim Hamby for his advice on XXX.

presentedat: This work was presented in the form of a poster at Forensics\@NIST on November 7, 2018 in Gaithersburg, Maryland

keywords:
- forensic science
- toolmark
- cross-correlation
- random forest
- 3d microscopy
- land engraved areas (LEAs)

@@

bibliography: bibliography
biblio-style: jfs

numsecdepth: 1

output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: template.tex
---

@@

@@

# Methods

<!-- ## Automated Processing of 3D Scans -->

@@

<!-- ## Statistics for Matching Aligned Signatures -->

@@

<!-- ## Interpreting the Algorithm Score -->

@@

<!-- ## Identification Errors and Algorithm Evaluation -->

@@

<!-- ## Assessing Match Strength -->
